\Large \bf Lissy: Experimenting with on-chain order books

### 2021-09-11 LaTeX-LNCS-2022/sections/paper.tex
adding a textblue

In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations. Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings). This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata. Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs. Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas. The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.  Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.

>>>>

In our \cm variant on Arbitrum, the validators do all computations (both enqueuing and dequeuing) so we choose to use a heap with dynamic array for our priority queue, which balances the expense of both operations. Heaps are 32\% more efficient than linked lists for submitting orders and 29\% less efficient for closing. Recall that without a roll-up, such a priority queue can only match 38 pairs at a cost of 5,372,679 gas. Table~\ref{tab:arbitrum_performance} shows that 38 pairs cost only 6,569 in L1 gas (a 99.88\% savings). This is the cost of submitting the \texttt{closeMarket()} transaction to the inbox to be recorded, which is 103 bytes of calldata. \textblue{Most importantly, \texttt{closeMarket()} always costs 6,569 even as the number of trades increase from 38 pairs to thousands or millions of pairs}. Of course, as the number of trades increase, the work for the validators on L2 increases, as measured in ArbGas. The price of ArbGas in Gwei is not well-established but is anticipated to be relatively cheap.  Arbitrum also reduces the costs for traders to submit an order: from 207,932 to 6,917 in L1 gas.
